Beating Simple Backtracking Search in Subgraph Algorithms\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/026842/1 and EP/M508056/1].}

### 2018-11-16 paper/paper.tex
Parallel is go

\title{Beating Simple Backtracking Search in Subgraph Algorithms\thanks{This work was
supported by the Engineering and Physical Sciences Research Council (grant numbers EP/026842/1 and
EP/M508056/1). This work used the Cirrus UK National Tier-2 HPC Service at EPCC
(http://www.cirrus.ac.uk) funded by the University of Edinburgh and EPSRC (EP/P020267/1).}}

\author{Blair Archibald\orcidID{????-????-????-????}\and
Ciaran McCreesh\orcidID{0000-0002-6106-4871}\and
Patrick Prosser\orcidID{0000-0003-4460-6912} \and
James Trimble\orcidID{0000-0001-7282-8745}}

\authorrunning{B. Archibald et al.}

@@

>>>>

\title{Sequential and Parallel Solution-Biased Search for Subgraph Algorithms\thanks{This work was
supported by the Engineering and Physical Sciences Research Council (grant numbers EP/P026842/1,
EP/M508056/1, and EP/N007565). This work used the Cirrus UK National Tier-2 HPC Service at EPCC
(http://www.cirrus.ac.uk) funded by the University of Edinburgh and EPSRC (EP/P020267/1).}}

\author{Blair Archibald\orcidID{0000-0003-3699-6658}\and
Ciaran McCreesh\orcidID{0000-0002-6106-4871}\and
Patrick Prosser\orcidID{0000-0003-4460-6912} \and
James Trimble\orcidID{0000-0001-7282-8745}}

%\authorrunning{B. Archibald et al.}

@@

    \includegraphics*{gen-graph-scatter-par.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-parconsttick.pdf}
